Consider this, you are middle age now with a family of four. One peaceful Sunday, you and your best mates decide to spend a great day out with all your families, bath on a remote beach, peddle the blue sparking water and ride the uncontained waves; weather is warm and beautiful, sun is just brilliant, you are setting up the barbie and everyone had a few drinks already, you are all enjoying the day and feel life can not be better than this. Suddenly, a sharp scream ratters the sky, as you are searching for the source, you see Michael, your friend, is rushing towards you, waving and shouting "Call 000, Ben needs help". As you jump up from your cosy beach chair, you see Ben is just dragged up by two guys and start to walking towards you, you searches for your mobile and dial 000. You are prompted to select ambulance service and confirm to send your GPS location, now you speak to one operator, by now you start to feel the adrenaline rush and you notice your voice is shaky. Just as you find difficult to complete a sentence, the operator asks whether Ben suffers heat attach and shows the symptoms of drowning. By now Ben is carried by mates and just stops in front of you under the beach umbrella, you walk towards Ben and you can see Ben is lack of movement and unconscious, you speak loudly into your mobile "yes, yes, Ben is not conscious", the operator assures you calmly "an ambulance is dispatched 10 mins ago and is currently 10 mins out from the scene" then the instruction continuous "please remain calm, does anyone know how to perform first aid, I need you now to lay Ben flat and check Ben's mouth is clean and airway is clear"; you ask around, you do not seem lucky this time, you say "no one trained in first aid, we don't have medical professional available now, I need more instructions." \\
A moment later, the instruction video starts to play on your mobile, you quickly put yourself together and follow closely to the steps: you open Ben's mouth and check Ben's airway is clear, you soon examine Ben's pulse. Ben seems having a shallow breath and uneven pulse, as you follow the instruction put Ben into recovery position the ambulance is arriving. Soon, Ben is with life supporting equipments, paramedics quickly cross check Ben's personal information with you and then ambulance disappears in the horizon. \\
On the way to emergency department, Ben has been stabilized and blood thinning medications have just been applied. Ben's breath and blood are now being sampled and screened for metabolites profile, which tells the biophysiological conditions about Ben's body at present moment. On the other side, emergency department has been busy preparing Ben's arrival one hour ago, since the moment Ben's life support system warned Ben's medical conditions and potential arrival. Now, if you read the lines carefully, you may wonder how ambulance service operator knew Ben's name, his location and Ben was in troubles, more importantly, how did they know you were calling to report about Ben's incident?  \\
Before we answer the questions, let's finish the story first. As Ben's arriving, emergency department is ready and duty doctors have been briefed with Ben's conditions, medical history and the accident; treatment plan has been laid out, discussed and agreed at this stage. Suddenly, alert bell rings, Ben's metabolic profile is in. Red alerts scatter across the screen, Ben shows the signs of artery blockage in addition to hyperglycemia with potential type II diabetics, Ben's metabolic profile also indicates Ben has toxin circulation which is likely introduced via jellyfish encounter, a well known cause to induce heart attack. In addition, Ben is also diagnosed with intolerance to aspiring, sulfate base medications. Emergency department quickly update the response plan to focus on  detoxicating Ben and reviving heart conditions. Ben escapes major artery damage luckily due to rapid rescue response. As Ben recovers in the ward, you and your mates visit him and his family for the first time, Ben l\\
Later in the day, Ben's blood profile is complete, doctor is having a conversation with Mel, Ben's wife, \\
Doctor: "Ben is in good condition and we suggest an observation period of another 24 hours before Ben can go home. Mel, have you noticed Ben has any discomfort recently?" \\
Mel: "I think, Ben has been talking he is not up to speed at work and Ben seems tired more often, also Ben do not seem to eat as much as before." \\
Doctor: "There is a high chance that Ben is at risk developing colorectal cancer, genetic and metabolic profile indicates Ben has some early sign of abnormality. We have discovered some genetic markers that run in the family" \\
Doctor calms Mel and continuous "Ben's genetic is at rarity, we simulated conventional measures against Ben's profile, it is likely to put additional burden on Ben's glucoregulatory and homeostatic balance, we will need to come up a new plan, I would like to refer Ben's case to our research department and they will take couple of months to analysis and suggest a remedy that tailed to Ben." \\
Mel thanked the doctor and asks: "What's the new remedy and will it is possible that children are at risk." \\
Doctor: "All medical interventions have side-effects, the idea is to cue the condition but put minimum stress on our patients, in Ben's case, Ben is less perceptible to stress on glucose regulatory system but our available coloratical medications put noticeable stress on glucose balance, we think this is not good for Ben's conditions. Our research team will design a remedy that can mediate Ben's coloratical risks and assert minimum pressure on Ben's existing conditions. Also we suspect the children will likely to inherit similar risk factors, I would suggest the kids to take a genetic profiling if they haven't done so, the preventative measures will go a long way." \\
You may be happy for Ben to escape a deadly medical condition without harm and you curious about the medical wonder on how can doctor tell Ben's coloratical conditions before any physiological symptoms, you may wonder how personalised medical treatment works and what is involved. In this book, we will reveal what is bioinformatics infused personalised medicine, what is the technology behind this capability and how informatics is revolutionising our medical research and practise, ultimately what is the future of our medicare system will look like.